DRAFT: v6.dev \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\

### 2025-04-01 main.tex
Paper updates from overleaf.

\title{
  DRAFT: v5 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}
% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
\author{
Gabriele Dell'Orto \and
Brecht Daams \and
Riender Happee \and
Georgios Papaioannou \and
Arjo J. Loeve \and
Jesper Meijerink \and
Thomas Valk \and
Jason K. Moore\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
}

@@

\color{red}
\section*{\centering Notice}
%
This draft report is not yet peer reviewed and is subject to change with
revisions. These results are preliminary, so we do not recommend relying on them
until a supporting peer reviewed paper is published.

\color{black}
\begin{abstract}
  Infants are transported in strollers and in baby seats mounted in cargo
  bicycles. The infants experience whole-body vibration during the associated
  walking and cycling trips, but there is little existing knowledge about
  associated comfort and health effects. To improve this, we measure the seat
  pan acceleration of five strollers and two styles of cargo bicycles with dummy
  infants representing ages 0 to 9 months over six different road surfaces of
  varying road roughness at typical travel speeds. The five strollers included
  three modern systems and two vintage systems with some level of suspension.
  One cargo bicycle had electric support enabling speeds up to 25~\si{\kph}. We
  report average seat pan acceleration for 78 different scenarios and
  investigate the effects of road surface, vehicle, seat type, and travel speed.
  Using the whole-body vibration ISO standards, we show that rough road
  surfaces, amplified by travel speed, may have health risks for travel
  durations as low as \SIrange{10}{30}{\min}. Stroller designs from 50 years ago
  significantly reduce vibrations, relative to most modern strollers we tested,
  indicating the need for return of suspension elements. Cargo bicycles ridden
  at the maximum electric bicycle speed over paver bricks can cause
  accelerations that should likely be avoided except for only the shortest of
  durations until more direct evidence of risks to infants is studied. Standards
  are needed for infant transport testing and evaluation, designers need to
  incorporate better suspension for infants, and research is needed to develop
  clear and direct connections to health and comfort effects.
\end{abstract}

@@

Schwanitz~et~al.~\cite{Schwanitz2020} assessed accelerations in a child bicycle
trailer riding over smooth asphalt, gravel, and cobblestones using ISO~2631-1
weighted RMS vertical accelerations.
Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
used as lumped masses. According to the results, tyre pressure and the number of
passengers had no significant effect on vibration magnitude, but road surface
and travel speed did. 
The baby sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
the toddler sized dummy (10~\si{\kilo\gram}), while the measured values
generally exceeded the ISO~2631-1 vibrational comfort of adults.
Rothhämel~et~al.~\cite{MalteChildComfort2022} conducted measurements using a
trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
asphalt and cobblestones for speeds between \SIrange{10}{20}{\kph}. 
After weighting the accelerations using ISO~2631-1 methods, they found a large
increase of the vibration amplitude on cobblestones compared to asphalt on the
same speed range. The child trailer exhibited larger weighted RMS accelerations
than the cargo bicycle with the child seat between the front wheels. 
Both the trailer and cargo bicycle child seats had generally larger magnitude
vibrations than experienced in an automobile seat travelling at 30~\si{\kph} on
a rough road \cite{gromadowski2013analysis}. Rothhämel and
Liu~\cite{rothhamel2023comfort} conducted measurements with a
6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
their values fell into the ``extremely uncomfortable'' zone for the ISO~2631-1.

@@

% Don't edit, working to change the following paragraph
In the context of infants transportation with stroller seats, Kok
Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
capture the vibrations transmitted onto the seat and backrest of a baby
stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
10.30~\si{\kilo\gram}. 
The comfort levels for the indoor testing were labelled as `Fairly
uncomfortable' to `A little uncomfortable', but the outdoor testing resulted in
`Extremely uncomfortable' and `Fairly uncomfortable' values. They used both a
child and dummy for the experiments, identifying similar patterns. However, the
results still consider ISO~2631-1 standard, which is designed for adults and
specific postures. In a similar research, Sierzputowski~
et~al.~\cite{sierzputowski2021pilot} investigated vibrations induced in a modern
and
an older stroller, when moving on different surfaces: asphalt road, concrete
paving blocks, concrete plates, dirt road, lawn and damaged concrete. The
obtained weighted RMS acceleration values based on ISO~2631-1 were several times
in the range of the highest discomfort ($>$2~\si{\mps\squared}). 
Another research which included also children as test subjects was conducted by
Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
children received, sitting upright in a stroller, when riding over a protrusion
(13x60 mm) with either one wheel or two wheels. 
The children were 3 to 6 years old, boys and girls, weighing
\SIrange{15.94}{19.96}{\kilo\gram} and measuring
\SIrange{98.0}{112.4}{\centi\meter} in length. 
Based on the results, the infant’s head and chest exhibit strong vibrations at
1~\si{\hertz} along all three axes (x,y and z), vibrate easily along the
y-direction at 2~\si{\hertz}, and are less likely to vibrate at more than
8~\si{\hertz}. 
This result is critical as this range of frequencies is very common in bicycles
and strollers. However, they did not assess the comfort and the health risk when
the children were exposed to these vibrations. 
Despite significant research on the effect of whole-body vibrations on
children's comfort, there is limited research on infants.

@@

\subsection{Postures}
%
All tested systems provided full support of back and head and allowed usage in
lying or at least reclined postures. Nine month old infants would be able to sit
erect but will often rest their heads or be asleep. Although sitting upright is
the best posture for children who can sit upright, a more reclined posture was
tested because this allowed measurement of vibration at the head-seat interface
while the head was always supported by the headrest. We tested all systems with
horizontal or reclined postures. The inclination angle with respect to the
ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
%
\begin{table}
  \centering
  \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
  each tested configuration. %We report the angles defined by the axis of the human body reference system (a reference system connected to the dummy, whose z-axis is aligned with the body spine and x-axis points to the front of the body) and the ground plane. 
  For the head 0~\si{\degree} means erect posture, and positive angles represent rearward head rotation with 90~\si{\degree} indicating a fully  supine posture (lying horizontally). For the seat pan I STILL DONT UNDERSTAND especially the -28 for Melia.}
\begin{tabular}{lllrrr}
\toprule
 &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
Vehicle Type & Model & Dummy & Baby seat (facing direction)& Seat Head & Seat Pan\\
\midrule
\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz (RF)& 41
& 2 \\
 &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
 &  & 3 mo & Melia (FF)& 64 & 2 \\
\cline{2-6}
 & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
 &  & 3 mo & Maxi-Cosi X Joolz (RF)& 49 & -43 \\
 &  & 3 mo & Melia (FF)& 64 & 2 \\
\cline{1-6} \cline{2-6}
\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot (RF)& 0 & 0\\
\cline{2-6}
 & Maxi-Cosi Street Plus & 9 mo & Baby seat (FF)& 40 & 10 \\
\cline{2-6}
 & Babyzen YOYO 0+ & 0 mo & Baby cot (RF)& 12 & 12 \\
\cline{2-6}
& Babyzen YOYO 6+ & 9 mo & Baby seat (FF)& 45 & 4 \\
\cline{2-6}
& Bugaboo Fox 5 & 0 mo & Baby cot (RF)& 0 & 0 \\
\cline{2-6}
 & Bugaboo Fox 5 & 9 mo & Baby seat (FF) & 49 & 24\\
\bottomrule
\end{tabular}
  \label{tab:baby-posture}
\end{table}

@@

\subsection{Trial Analyses}
%
Figure~\ref{fig:vert-acc-example} shows an example time history of the vertical
acceleration of the seat pan during a single repetition. To perform the
ISO~2631-1 recommended health and comfort analysis, we first downsampled the
time history from the hardware-set variable sampling frequency of approximately
910.22~\si{\hertz} to a constant sample rate of 400~\si{\hertz} using linear
interpolation, giving sufficient samples for the bandwidth of interest based on
the Nyquist frequency. We set any acceleration values outside of the sensor
manufacturer's reported operating range of \(\pm\)16~g to that maximum or
minimum, respectively, given that values outside the range may be unreliable.
Values that exceed the range are rare and only present in some of the cargo
bicycle paver brick trials, but are common in the shock tests. Following the
ISO~2631-1 recommendation, we low-pass filtered the signal at
\(1.5\times80~\si{\hertz}=120~\si{\hertz}\) using a zero-lag
2\textsuperscript{nd} order Butterworth filter, given that the standard only
applies to frequencies up to 80~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session001-t2-aula-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
  \caption{Raw seat pan vertical acceleration versus time from session 001:
  Maxi-Cosi Street Plus Stroller over the Sidewalk Slabs. Black horizontal lines
  indicate the \(\pm\)root mean square (RMS) about the mean and grey horizontal
  lines indicate the \(\pm\)vibration dose value (VDV) about the mean.}
  \label{fig:vert-acc-example}
\end{figure}

ISO~2631-1 provides weighting filters that highlight those frequencies adults
are most sensitive to. To apply them, we calculated the amplitude spectra of the
acceleration time histories of each trial using the Fast Fourier Transform
(FFT). Figure~\ref{fig:freq-spectrum} gives an example of a raw amplitude
spectrum along with smoothened versions of the raw and ISO 2631-1 weighted
signals. In almost all trials, there is a single dominant peak frequency in the
ISO weighted and smoothed spectra. For the few trials that had two or more peaks
at approximately the same amplitude, the second peak was sometimes selected.
After ISO weighting, the area under the spectrum curve was calculated and the
frequency below which 80\% of the amplitude content falls marked as an indicator
of bandwidth.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
  \caption{Seat pan vertical acceleration amplitude spectrum from session 004:
  Maxi-Cosi Street Plus over cobblestones. The gray curve shows the result of
  the FFT, the black line is a smoothed version of the FFT (zero-lag Butterworth
  low pass), and the blue line is the smoothed ISO weighted FFT. The blue dashed
  vertical line indicates the frequency at the maximum amplitude of the smoothed
  curve. The blue dashed-dotted vertical line indicates the bandwidth threshold
  for 80\% of the area under the blue curve.}
  \label{fig:freq-spectrum}
\end{figure}

@@

\begin{align}
  \textrm{VDV}_{a_{z}} = \left(\frac{1}{M}\sum_{m=1}^{M} a_{z}^4(t_m)\right)^{1/4}
  \label{eq:vdv-acc}
\end{align}

@@

\subsection{Effect of Dummy Size}
%
Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
acceleration for each repetition for all vehicles, comparing among dummy sizes.
There were larger accelerations in the bicycle (high speeds) versus the stroller
(low speeds), likely mostly attributed to the different testing speeds. When
comparing the vertical RMS acceleration values between cargo bicycles and
strollers there are no obvious differences due to baby size, i.e. each dummy
size experienced a similar range of acceleration magnitudes when vehicle type
and road surface are ignored. For the bicycles, the lightest dummy sometimes
experienced higher acceleration than the heavier dummy, but high and low
accelerations are seen across the speed range tested.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
  baby age (and thus size \& mass) for all repetitions with colour indicating
  the mean speed of the trial. The lightest colour dots are strollers and the
  remaining are cargo bicycles.}
  \label{fig:compare-baby-mass}
\end{figure}

@@

@@

\subsection{Shock}
%
We identified the maximum peak acceleration values for each trial
(Equation~\ref{eq:max-acc}), then averaged them across repetitions to obtain the
results listed in Table~\ref{tab:shock} for different vehicles and
configurations. There is a significant variation among tests, with the peaks for
the bicycles sometimes reaching the accelerometer's full scale (\(\pm\)16~g).
While the seat pan accelerations for the strollers are generally lower than
those experienced with the bicycles, the configuration (0 or 9 months) may play
a large role. Among bicycles, the use of Melia baby shell seems to transmit
lower accelerations compared to Maxi-Cosi, 3 months, for both the Keiler
tricycle and the Urban Arrow. Strollers with the baby seat configuration for 9
months show much lower acceleration compared to the baby cot for 0 months
(Bugaboo and Maxi-Cosi). Surprisingly, the oldest strollers (Old Rusty and Green
Machine) performed very well during the shock test, resulting in the lowest seat
pan acceleration among all the tested vehicles.
Figure~\ref{fig:shock_vehicle_comparison} shows the peaks of the vertical
acceleration recorded at the seat pan, grouped by different vehicles, for the
shock test. As noted in Table~\ref{tab:shock}, the old strollers Old Rusty and
Green Machine show lower acceleration values. We do not clearly distinguish any
trend with speed for the bicycles (Keiler and Urban Arrow). During the tests
involving Keiler tricycle and strollers, we cannot exclude that the front wheels
(left and right) hit the bump at slightly different time instants.   
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-shock-test-compare.png}
  \caption{Vertical acceleration recorded at the seat pan during the shock test
  per each trial, grouped by vehicles. The colour indicates the mean speed of
  the trial. The lighter the colour the lower the speed.}
  \label{fig:shock_vehicle_comparison}
\end{figure}

@@

@@

Table~\ref{tab:results} shows the mean over the scenario repetitions unweighted
and ISO~2631-1 weighted seat pan vertical RMS acceleration, unweighted seat pan
vertical VDV, crest factor, peak frequency, bandwidth, and duration for all 52

@@

% NOTE : This table is generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!

@@

  \caption{Mean computed metrics for all 52 non-shock scenarios, using seat pan
  vertical accelerations.}
  \label{tab:results}

@@

\begin{tabular}{lllccccccccc}

@@

        &            &         & Target & Trial     & RMS     & ISO Weighted & VDV      & Crest  & Peak      & \\
        &            & Road    & Speed  & Count     & Accel   & RMS Accel    & Accel    & Factor & Freq. & Bandwidth  & Duration \\
Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\

@@

\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 6.6 & 6.2 & 6.5 & 14.3 & 20.4 \\
\cline{3-12}
 &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 3.4 & 4.1 & 9.5 & 17.2 & 23.3 \\
\cline{3-12}
 &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 7.5 & 13.5 & 6.1 & 18.5 & 25.4 \\
\cline{3-12}
 &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 7.9 & 6.4 & 5.8 & 15.1 & 20.2 \\
\cline{3-12}
 &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.9 & 3.3 & 10.1 & 18.5 & 23.1 \\
\cline{2-12} \cline{3-12}
 & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 3.4 & 4.7 & 6.6 & 20.7 & 22.5 \\
\cline{3-12}
 &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 3.0 & 3.8 & 9.4 & 26.4 & 22.6 \\
\cline{3-12}
 &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 2.5 & 5.5 & 7.7 & 23.8 & 24.7 \\
\cline{3-12}
 &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 3.6 & 5.3 & 6.0 & 20.3 & 24.5 \\
\cline{3-12}
 &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.8 & 6.5 & 8.4 & 29.3 & 34.6 \\
\cline{1-12} \cline{2-12} \cline{3-12}
\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 4.6 & 5.3 & 4.1 & 17.3 & 23.7 \\
\cline{3-12}
 &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 2.1 & 4.5 & 4.2 & 26.8 & 29.6 \\
\cline{3-12}
 &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 4.2 & 6.5 & 4.1 & 18.5 & 28.2 \\

>>>>

\title{
  DRAFT: v6.dev \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}
% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
\author{
Gabriele Dell'Orto \and
Brecht Daams \and
Riender Happee \and
Georgios Papaioannou \and
Arjo J. Loeve \and
Jesper Meijerink \and
Thomas Valk \and
Jason K. Moore\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
}

@@

\color{red}
\section*{\centering Notice}
%
This draft report is not yet peer-reviewed and is subject to change with
revisions. These results are preliminary, so we do not recommend relying on them
until a supporting peer-reviewed paper is published.

\color{black}
\begin{abstract}
  Infants are transported in strollers and in baby seats mounted on cargo
  bicycles. The infants experience whole-body vibration during the associated
  walking and cycling trips, but there is little existing knowledge about
  associated comfort and health effects. To improve this, we measure the seat
  pan acceleration of five strollers and two styles of cargo bicycles with dummy
  infants representing ages 0 to 9 months over six different road surfaces of
  varying road roughness at typical travel speeds. The five strollers included
  three modern systems and two vintage systems with some level of suspension.
  One cargo bicycle had electric support enabling speeds up to 25~\si{\kph}. We
  report average seat pan acceleration for 78 different scenarios and
  investigate the effects of road surface, vehicle, seat type, and travel speed.
  Using the whole-body vibration ISO standards, we show that rough road
  surfaces, amplified by travel speed, may have health risks for travel
  durations as low as \SIrange{10}{30}{\min}. Stroller designs from 50 years ago
  significantly reduce vibrations, relative to most modern strollers we tested,
  indicating the need for a return of suspension elements. Cargo bicycles ridden
  at the maximum electric bicycle speed over paver bricks can cause
  accelerations that should likely be avoided except for only the shortest of
  durations until more direct evidence of risks to infants is studied. Standards
  are needed for infant transport testing and evaluation, designers need to
  incorporate better suspension for infants, and research is needed to develop
  clear and direct connections to health and comfort effects.
\end{abstract}

@@

Schwanitz~et~al.~\cite{Schwanitz2020} assessed accelerations in a child bicycle
trailer riding over smooth asphalt, gravel, and cobblestones using ISO~2631-1
weighted RMS vertical accelerations.
Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
used as lumped masses to represent the child body. According to the results, tyre pressure and the number of
passengers had no significant effect on vibration magnitude, but road surface
and travel speed did. 
The baby sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
the toddler sized dummy (10~\si{\kilo\gram}), while the measured values
generally exceeded the ISO~2631-1 vibrational comfort of adults.
Rothhämel~et~al.~\cite{MalteChildComfort2022} conducted measurements using a
trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
asphalt and cobblestones for speeds between \SIrange{10}{20}{\kph}. 
After weighting the accelerations using ISO~2631-1 methods, they found a large
increase of the vibration amplitude on cobblestones compared to asphalt on the
same speed range. The child trailer exhibited larger weighted RMS accelerations
than the cargo bicycle with the child seat between the front wheels. 
Both the trailer and cargo bicycle child seats had generally larger magnitude
vibrations than experienced in an automobile seat travelling at 30~\si{\kph} on
a rough road \cite{gromadowski2013analysis}. Rothhämel and
Liu~\cite{rothhamel2023comfort} conducted measurements with a
6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
their values fell into the ``extremely uncomfortable'' zone for the ISO~2631-1.

@@

% Don't edit, working to change the following paragraph
In the context of infants transportation with stroller seats, Kok
Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
capture the vibrations transmitted onto the seat and backrest of a baby
stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
10.30~\si{\kilo\gram}. 
The comfort levels for the indoor testing were labelled as `Fairly
uncomfortable' to `A little uncomfortable', but the outdoor testing resulted in
`Extremely uncomfortable' and `Fairly uncomfortable' values. They used both a
child and dummy for the experiments, identifying similar patterns. However, the
results still consider ISO~2631-1 standard, which is designed for adults and
specific postures. In a similar research, Sierzputowski~
et~al.~\cite{sierzputowski2021pilot} investigated vibrations induced in a modern
and
an older stroller, when moving on different surfaces: asphalt road, concrete
paving blocks, concrete plates, dirt road, lawn and damaged concrete. The
obtained weighted RMS acceleration values based on ISO~2631-1 were several times
in the range of the highest discomfort ($>$2~\si{\mps\squared}). 
Another research which also included children as test subjects was conducted by
Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
children received, sitting upright in a stroller, when riding over a protrusion
(13x60 mm) with either one wheel or two wheels. 
The children were 3 to 6 years old, boys and girls, weighing
\SIrange{15.94}{19.96}{\kilo\gram} and measuring
\SIrange{98.0}{112.4}{\centi\meter} in length. 
Based on the results, the infant’s head and chest exhibit strong vibrations at
1~\si{\hertz} along all three axes (x,y and z), vibrate easily along the
y-direction at 2~\si{\hertz}, and are less likely to vibrate at more than
8~\si{\hertz}. 
This result is critical as this range of frequencies is very common in bicycles
and strollers. However, they did not assess the comfort and the health risk when
the children were exposed to these vibrations. 
Despite significant research on the effect of whole-body vibrations on
children's comfort, there is limited research on infants.

@@

\subsection{Postures}
%
All tested systems provided full support of back and head and allowed usage in
lying or at least reclined postures. Nine month old infants would be able to sit
erect but will often rest their heads or be asleep. Although sitting upright is
the best posture for children who can sit upright, a more reclined posture was
tested because this allowed measurement of vibration at the head-seat interface
while the head was always supported by the headrest. We tested all systems with
horizontal or reclined postures. The inclination angle with respect to the
ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
%
\begin{table}
  \centering
  \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
  each tested configuration. %We report the angles defined by the axis of the human body reference system (a reference system connected to the dummy, whose z-axis is aligned with the body spine and x-axis points to the front of the body) and the ground plane. 
  For the head positive angles represent forward head rotation with 0~\si{\degree} indicating a fully  supine posture (lying horizontally) and 90~\si{\degree} fully erect. For the seat pan  0~\si{\degree} is horizontal and positive angles indicate elevated legs, see Figures in Appendix \ref{app:equipment}. I STILL DONT UNDERSTAND -43. RF is rearward facing and FF is forward facing.}
\begin{tabular}{lllrrr}
\toprule
 &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
Vehicle Type & Model & Dummy & Baby seat (facing direction)& Head & Seat Pan\\
\midrule
\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz (RF)& 41
& 2 \\
 &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
 &  & 3 mo & Melia (FF)& 64 & 2 \\
\cline{2-6}
 & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
 &  & 3 mo & Maxi-Cosi X Joolz (RF)& 49 & -43 \\
 &  & 3 mo & Melia (FF)& 64 & 2 \\
\cline{1-6} \cline{2-6}
\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot (RF)& 0 & 0\\
\cline{2-6}
 & Maxi-Cosi Street Plus & 9 mo & Baby seat (FF)& 40 & 10 \\
\cline{2-6}
 & Babyzen YOYO 0+ & 0 mo & Baby cot (RF)& 12 & 12 \\
\cline{2-6}
& Babyzen YOYO 6+ & 9 mo & Baby seat (FF)& 45 & 4 \\
\cline{2-6}
& Bugaboo Fox 5 & 0 mo & Baby cot (RF)& 0 & 0 \\
\cline{2-6}
 & Bugaboo Fox 5 & 9 mo & Baby seat (FF) & 49 & 24\\
\bottomrule
\end{tabular}
  \label{tab:baby-posture}
\end{table}

@@

\subsection{Trial Analyses}
%
Figure~\ref{fig:vert-acc-example} shows an example time history of the vertical
acceleration of the seat pan during a single repetition. To perform the
ISO~2631-1 recommended health and comfort analysis, we first downsampled the
time history from the hardware-set variable sampling frequency of approximately
910.22~\si{\hertz} to a constant sample rate of 400~\si{\hertz} using linear
interpolation, giving sufficient samples for the bandwidth of interest based on
the Nyquist frequency. We set any acceleration values outside of the sensor
manufacturer's reported operating range of \(\pm\)16~g to that maximum or
minimum, respectively, given that values outside the range may be unreliable.
Values that exceed the range are rare and only present in some of the cargo
bicycle paver brick trials, but are common in the shock tests. Following the
ISO~2631-1 recommendation, we low-pass filtered the signal at
\(1.5\times80~\si{\hertz}=120~\si{\hertz}\) using a zero-lag
2\textsuperscript{nd} order Butterworth filter, given that the standard only
applies to frequencies up to 80~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session001-t2-aula-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
  \caption{Raw seat pan vertical acceleration versus time from session 001:
  Maxi-Cosi Street Plus Stroller over the Sidewalk Slabs. Black horizontal lines
  indicate the \(\pm\)root mean square (RMS) about the mean. The vibration dose
  value (VDV) for the printed duration is shown in the bottom left.}
  \label{fig:vert-acc-example}
\end{figure}

ISO~2631-1 provides weighting filters that highlight those frequencies adults
are most sensitive to. To apply them, we calculated the amplitude spectra of the
acceleration time histories of each trial using the Fast Fourier Transform
(FFT). Figure~\ref{fig:freq-spectrum} gives an example of a raw amplitude
spectrum along with smoothened versions of the raw and ISO 2631-1 weighted
signals. In almost all trials, there is a single dominant peak frequency in the
ISO weighted and smoothed spectra. For the few trials that had two or more peaks
at approximately the same amplitude, the second peak was sometimes selected.
After ISO weighting, the area under the spectrum curve was calculated and the
frequency below which 80\% of the amplitude content falls marked as an indicator
of bandwidth.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
  \caption{Seat pan vertical acceleration amplitude spectrum from session 004:
  Maxi-Cosi Street Plus over cobblestones. The gray curve shows the result of
  the FFT, the black line is a smoothed version of the FFT (zero-lag Butterworth
  low pass), and the blue line is the smoothed ISO weighted FFT. The blue dashed
  vertical line indicates the frequency at the maximum amplitude of the smoothed
  curve. The black dashed-dotted vertical line indicates the bandwidth threshold
  for 80\% of the area under the black curve.}
  \label{fig:freq-spectrum}
\end{figure}

@@

\begin{align}
  \textrm{VDV}_{a_{z}} = \left[\sum_{m=2}^{M} \frac{1}{2} (a_{z,m}^4 - a_{z,m-1}^4) (t_m -t_{m-1})\right]^{1/4}
  \label{eq:vdv-acc}
\end{align}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-spectra-compare.png}
  \caption{Mean amplitude spectra of each vehicle.} 
  \label{fig:spectra-compare}
\end{figure}

@@

@@

\section{Exploratory Statistics}
%
\subsection{Effect of Dummy Size}
%
Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
acceleration for each repetition for all vehicles, comparing among dummy sizes.
There were larger accelerations in the bicycle (high speeds) versus the stroller
(low speeds), likely mostly attributed to the different testing speeds. When
comparing the vertical RMS acceleration values between cargo bicycles and
strollers there are no obvious differences due to baby size, i.e. each dummy
size experienced a similar range of acceleration magnitudes when vehicle type
and road surface are ignored. For the bicycles, the lightest dummy sometimes
experienced higher acceleration than the heavier dummy, but high and low
accelerations are seen across the speed range tested.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
  baby age (and thus size \& mass) for all repetitions with colour indicating
  the mean speed of the trial. The lightest colour dots are strollers and the
  remaining are cargo bicycles.}
  \label{fig:compare-baby-mass}
\end{figure}

@@

Table~\ref{tab:summary-stroller} and Table~\ref{tab:summary-bicycle} show mean
values over the scenario repetitions. They report the unweighted and ISO~2631-1
weighted seat pan vertical RMS acceleration, weighted seat pan magnitude RMS
acceleration, unweighted seat pan vertical VDV for the first 10 seconds of the
reptition, crest factor, peak frequency, bandwidth, and duration for all 67

@@

% NOTE : These tables are generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!

@@

  \caption{Mean computed metrics of the strollers for all 40 non-shock
  scenarios, using seat pan acceleration.}
  \label{tab:summary-stroller}

@@

\begin{tabular}{lllcccccccccc}

@@

        &            &         &        & .     &     & ISO      & ISO      &     &        &      &       &       \\
        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\

@@

\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 4.5 & 11.5 & 6.2 & 6.5 & 20.5 & 20.4 \\
\cline{3-13}
 &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 2.5 & 6.1 & 4.1 & 9.5 & 23.4 & 23.3 \\
\cline{3-13}
 &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 2.9 & 15.6 & 13.5 & 6.1 & 49.8 & 25.4 \\
\cline{3-13}
 &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 4.8 & 12.5 & 6.4 & 5.8 & 30.6 & 20.2 \\
\cline{3-13}
 &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.7 & 1.7 & 3.3 & 10.1 & 33.3 & 23.1 \\
\cline{2-13} \cline{3-13}
 & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 2.5 & 6.2 & 4.7 & 6.6 & 37.9 & 22.5 \\
\cline{3-13}
 &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 1.8 & 5.2 & 3.8 & 9.4 & 43.2 & 22.6 \\
\cline{3-13}
 &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 1.6 & 4.5 & 5.5 & 7.7 & 39.5 & 24.7 \\
\cline{3-13}
 &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 2.3 & 5.9 & 5.3 & 6.0 & 36.6 & 24.5 \\
\cline{3-13}
 &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.5 & 1.6 & 6.5 & 8.4 & 51.2 & 34.6 \\
\cline{1-13} \cline{2-13} \cline{3-13}
\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 3.4 & 7.2 & 5.3 & 4.1 & 38.1 & 23.7 \\
\cline{3-13}
 &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 1.6 & 3.2 & 4.5 & 4.2 & 47.4 & 29.6 \\
\cline{3-13}
